
%-------------------------
% Resume in Latex
% Author : Jesus Arias
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage[sfdefault]{carlito}
% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Jesus Arias} \\ \vspace{2pt}
    \small 480-939-1780 $|$ \href{mailto:jeariaas@gmail.com}{\underline{jeariaas@gmail.com}} $|$ 
    \href{https://linkedin.com/in/arias-jesus}{\underline{linkedin.com/in/arias-jesus}} $|$
    \href{https://github.com/jeariaas}{\underline{github.com/jeariaas}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Arizona}{Aug. 2019 -- May 2023}
      {Bachelor of Science in Electrical and Computer Engineering, Minor in Mathematics}{Tucson, AZ}
  \resumeSubHeadingListEnd
   \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Courses}{: Computer Architecture and Design I \& II, Advanced Object Oriented Software I \& II, Data Structures \& Algorithms, Embedded Systems Design,
      Microprocessor Organization, Computational Techniques, Circuit Analysis, Systems Engineering Process, Semiconductor Processing, Digital VLSI Design, Computer Networking} \\
    }}
 \end{itemize}
  

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software \& Reliability Engineer I}{Jun. 2023 -- Present}
      {Microchip Technology Inc.}{Chandler, AZ}
      \resumeItemListStart
        \resumeItem{Developed a Python script automating MTBFIT data parsing, reducing creation time from 2 weeks to 10 minutes.}
        \resumeItem{Implemented a file storage system migrating burn-in recipes to a document library used by all MCHP sites.}
        \resumeItem{Directed the development and implementation of 3D printing capabilities in the Reliability department.}
        \resumeItem{Supported Reliability sub-departments in modeling and printing high-temperature withstanding test items.}
        \resumeItem{Designed multi-layer high pin-out breakout boards in Altium supporting ESD qualification testing. }
        \resumeItem{Operated advanced Burn-In systems achieving a 15\% decrease in handling failures during qualification.
        \newline - ELES smART, ELES TTS1, ELES MTx, MCC-LC2, and AEHR Max2/Max3 ovens.}
        \resumeItem{Created a Python script converting AEHR Burn-In programs to MCC-LC2 Burn-In programs.}
        \resumeItem{Researched, submitted, and presented 30+ Burn-In Specification reports to engineers and customers.}
        \resumeItem{Released 10+ Product and Package Qualification reports for DCS, CBU, MPD, MCU08 and MCU16.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Example Company}
%          {Example text}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineering Intern}{May 2021 -- May 2023}
      {IBM Corporation}{Tucson, AZ}
      \resumeItemListStart
        \resumeItem{Assisted in development of a diagnostic server-health evaluation bash script.}
        \resumeItem{Deployed code to over 4,000 XIV/A9000/R flash storage systems identifying potential failing BBU power supplies.
        \newline - Negated over 10,000 potential replacements for over 600 companies.}
        \resumeItem{Contributed as a software engineer in an Agile environment, improving existing software and unit testing.}
        \resumeItem{Diagnosed technical issues and supported clients in resolving issues related to XIV/A9000/R storage servers.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Let's Boil a Computer, Again! - Hardware and Software Team Lead} }{Aug. 2022 -- May 2023}
          \resumeSubSubheading{Senior Design Capstone @ The University of Arizona for Microsoft Corporation}{Tucson, AZ}
          \resumeItemListStart
            \resumeItem{Prototyped and constructed a Two-Phase Immersion Cooling server for Microsoft using FC-72 Fluorinert.}
            \resumeItem{Designed and coded a Graphical User Interface using Tkinter in Python for system and sensor control.}
            \resumeItem{Implemented and integrated a multi-threaded dynamically updating dual-axis graph using Matplotlib onto the Python GUI from realtime C++ embedded sensor data.}
            \resumeItem{Directed total system design total system wiring, and total system construction by researching best practices and documenting all decisions made into a public Codex repository available for view.}
            \resumeItem{Received Best Design, Project, and Presentation popular vote during Craig M. Berge Senior Capstone Design Day.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{CatDash - Campus Food Delivery Service Interface} }{Aug. 2022 -- May 2023}{}
          \resumeItemListStart
            \resumeItem{Prototyped and constructed a Two-Phase Immersion Cooling server for Microsoft using FC-72 Fluorinert.}
            \resumeItem{Received Best Design, Project, and Presentation popular vote during Craig M. Berge Senior Capstone Design Day.}
            \resumeItem{Received Best Design, Project, and Presentation popular vote during Craig M. Berge Senior Capstone Design Day.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{CatDash - Campus Wide Food Delivery Service Interface} }{Aug. 2022 -- May 2023}{}
          \resumeItemListStart
            \resumeItem{Prototyped and constructed a Two-Phase Immersion Cooling server for Microsoft using FC-72 Fluorinert.}
            \resumeItem{Received Best Design, Project, and Presentation popular vote during Craig M. Berge Senior Capstone Design Day.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Let's Boil a Computer, Again! - Hardware and Software Team Lead} }{Aug. 2022 -- May 2023}{}
          \resumeItemListStart
            \resumeItem{Prototyped and constructed a Two-Phase Immersion Cooling server for Microsoft using FC-72 Fluorinert.}
            \resumeItem{Received Best Design, Project, and Presentation popular vote during Craig M. Berge Senior Capstone Design Day.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.22in, label={}]
    \small{\item{
     \textbf{Skills}{: Python, C/C++, Java, JavaScript, HTML/CSS, React, R, MatLab, Git, Github, Altium, LaTeX, Microsoft Power Automate, Circuit Design, Soldering, Micro-Soldering, PCB Design} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
