
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jesus Arias} \\ \vspace{1pt}
    \small 480-939-1780 $|$ \href{mailto:x@x.com}{\underline{jeariaas@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/arias-jesus}} $|$
    \href{https://github.com/...}{\underline{github.com/jearias}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Arizona}{Aug. 2019 -- May 2023}
      {Bachelor of Science in Electrical and Computer Engineering, Minor in Mathematics}{Tucson, AZ}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Computer Reliability Engineer}{Jun. 2023 -- Present}
      {Microchip Technology Inc.}{Chandler, AZ}
      \resumeItemListStart
        \resumeItem{Developed a Python based automation script to parse and calculate MTBFIT data from quarterly Reliability
        Monitoring Reports reducing manual report creation time from 2 weeks to 10 minutes. Featuring: Directory file selection, Precise data separation and requisition,
        Streamlined JSON conversion for efficient storage, and Automatic file creation timestamping.}
        \resumeItem{Operated and managed advanced burn-in systems: ELES smART, ELES TTS1, ELES MTx, MCC-LC2, and
        AEHR Max2/Max3 ovens, achieving a 15\% decrease in failures during product testings over 1 year.}
        \resumeItem{Created an AEHR to MCC-LC2 Python based burn-in program conversion script improving workflow
        efficiency, decreasing time between tests, and increasing cross-platform compatibility between burn-in systems.}
        \resumeItem{Researched, submitted, and presented 30+ Burn-In Specification reports and solely released 10+ Product and Package Qualification reports 
        for Microchip's two most profitable and important business units: Data Center Solutions (DCS) and Communications Business Unit (CBU).}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineering Intern}{May 2021 -- May 2023}
      {IBM Corporation}{Tucson, AZ}
      \resumeItemListStart
        \resumeItem{Assisted in development of a diagnostic health evaluation bash script deployed to over 4,000
        XIV/A9000/R flash storage systems to identify potential failing BBU power supplies.}
        \resumeItem{Implemented the bash script over remote connection with customers negating the need for over 10,000 physical BBU power supplies
        replacements for over 600 companies worldwide, saving critical information from being lost and preventing millions of dollars in down time from occuring.}
        \resumeItem{Diagnosed technical issues and supported clients in resolving issues related to XIV/A9000/R
        flash storage servers.}
    \resumeItemListEnd

    \resumeSubheading
      {I.T. Support Volunteer and Guide} {Summers 2019 - 2023}
      {Arizona Museum of Natural History}{Mesa, AZ}
      \resumeItemListStart
        \resumeItem{Upgraded legacy computers with new hardware and upgraded software to Office 365 for enhanced efficiency.}
        \resumeItem{Conducted I.T. training to educate volunteers on new applicable software like Zoom, Teams, and Office 365 suite.}
        \resumeItem{Implemented and managed the technology infastructure for virtual tours, webinars, and online educational programs using Zoom and WebEx.}
        \resumeItem{Set up automated systems for inventory management and scheduling using Microsoft Power Automate.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Let's Boil a Computer, Again! - Hardware and Software Team Lead} }{Aug. 2022 -- May 2023}
          \resumeSubSubheading{Senior Design Capstone @ The University of Arizona for Microsoft Corporation}{Tucson, AZ}
          \resumeItemListStart
            \resumeItem{Prototyped and constructed a Two-Phase Immersion Cooling server for Microsoft using FC-72 Fluorinert.}
            \resumeItem{Designed and coded a Graphical User Interface using Tkinter in Python for system and sensor control.}
            \resumeItem{Implemented and integrated a multi-threaded dynamically updating dual-axis graph using Matplotlib onto the Python GUI from realtime C++ embedded sensor data.}
            \resumeItem{Directed total system design total system wiring, and total system construction by researching best practices and documenting all decisions made into a public Codex repository available for view.}
            \resumeItem{Received Best Design, Project, and Presentation popular vote during Craig M. Berge Senior Capstone Design Day.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Relevant Coursework and Technical Skills}
 \begin{itemize}[leftmargin=0.22in, label={}]
    \small{\item{
      \textbf{Courses}{: Computer Architecture and Design I \& II, Advanced Object Oriented Software I \& II, 
      Microprocessor Organization,  Computational Techniques, Systems Engineer Process, Semiconductor Processing, Digital VLSI Design} \\
     \textbf{Languages}{: Python, C/C++, Java, JavaScript, HTML/CSS, R, MatLab} \\
     \textbf{Developer Tools}{: Git, Github, VSCode, PyCharm, Eclipse, Altium, LaTeX} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Tkinter, Plotly, OpenCV, Beautiful Soup}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
